Resume of Chia-Hung Carlos Ma
⾺嘉鴻/0919155809/⾼雄市鳳⼭區龍成路92-2號
/Q123362294/11061982
Experience of Jobs
• TaiGen Vehicle Electronics[military technology substitute service]/firmware
and power electronics engineer/2 Months
• Can Bus protocol implementation on Microchip DSPic/PMSM analog drive
circuit design/Dev. of algorithm to reduce armature reaction of motor.
• Quit for serve chronic migraine after spine operation and transferred to military
substitute service by related authority of Taiwan government.
• Military Substitute Service/Traffic management Station at Taitung, Taiwan/
half year
• Dev. of excel VBA app for all employees food subscribe and crawler for gov.
routine tasks automation/VBA for subscribe Taiwan railways ticket automation/
VBA for many kinds of reports automation generator of gov. institutes.
• National Sun Yat-Sen University/Research Assistant/Half year
• Power and Conditioner control and schedule system for library and IT center/
modify website version virtualbox of single user ver. to have capabilities to be
used for every student in school/JQuery and Ajax/PHP/learned GNU_Linux
operations/DBMS/PLC ladder diagram programming/javascript.
• Quit to back to private enterprise for recovery of chronic migraine and want to
learn techniques of embedded system.
• Kaohsiung branch of PlusTek/software and firmware engineer/2 years
• TI DVR embedded system dev./Dev. GUI of Faraday Tech.'s DVR to meet the
Spec. from PM with China's miniGUI and fixed the bugs and unfinished
features of miniGUI on circumstance without support/IPC techniques/data
⾴尾 1structures study/learned the boot process of GNU/Linux on arm and x86
platforms/
• Quit for unpredictable passing of the exam of CSBC IT engineer without any
preparation and my parents forced me to be on board because my father has
worked at CSBC about 40 years.
• CSBC[taiwan](china ship building company owned by Taiwan government )/
software engineer/one year
• CRUD websites coding with asp.net/mechanism automation design system for
ship building.
• Quit for felt wasting life and bored in enterprise owned by gov. and friends
known in NTU invited me to Luxgen to design controller of hybrid vehicles
• Luxgen Vehicle Manufacturing/firmware and PMSM control engineer/one
year
• Quit for friends in NTU all leaved.
• Atrust Computer[funded by founder of HTC]/firmware and software
engineer/2 years
• cmake/refactor and dev. Bash scripts on thin clients firmware management on
arm and x86 platforms/thin clients c++ Qt apps sustaining and modification/
dev. of firmware image generator Scripts.
• Fired for narcolepsy without cataplexy happened and doctors think it’s
triggered by the spine operation years ago.
• So far, it’s under control for taking expensive medicine per day paid by Taiwan
health insurance.
• Anjia and GPlus IoT companies/software and embedded engineer/Half year
• ERP system dev. for employees on Social care system for olders and disabled
persons/flask for GYM CRM(side project)/setup all IT systems with dockers.
⾴尾 2• Quit for CEO and some employees broke the laws and sentenced guilty on
cheating on applying Taiwan government’s money. After quitting, I applied the
phd program of NCKU CSIE for desiring to know more about operating system
softwares.
• Jiaokun technology[founded by myself]/RD manager/above 2 year
• git actions CI/CD and nodejs express framework tutorials for CSIE students of
NTOU/RISC-V cpu, capabilities of superscaler and out of order, dev. by chisel
instead of verilog/study compiler engineering/setup and testing VLAN/phased
array Antenna and sonar design dev. TMU biotech embedded system dev.
Displayport related digital FPGA design. Factory automation system design.
Experience of Education
• Bachelor: Mechanical engineering, National central university at ChungLi,
Taoyun, Taiwan.
• Debate club and won the national universities debate competition 4th award.
• Master: System control division, Mechanical Engineering, national Taiwan
university at Taipei,Taiwan.
• Verilog Digital FPGA programming/8051/Brushed DC motor torque control
drive and algorithm design/digital high,low and band pass filter design/hybrid
scooter mechanism design/engine digital control/hybrid scooter dynamics
simulation on matlab for seizing the best algorithm
• PhD: operation system lab, computer science and information engineering,
National Chang-Kung University at Tainan, Taiwan. Drop after a half year.
Personality and habits
• Paranoid and aggressive at coding and IT and circuits techniques study.
• Jogging and weight training/joined few half marathon races and 4kms jogging
about 3 times/week.
⾴尾 3• Having thought that managing team relationship is harder than technology skills
study and preferred work alone.
• Loving studying medical ,economics, politics and psychology related books.
e.g. books of anatomy, mental health, psychology, justice, 貨幣銀行學, 為什麼我們的錢變薄了(1970s) and etc.